Category-Pivot Transfer Learning from Knowledge Base to Microblog Stream for Accurate Event Detection

### 2016-10-02 paper/lncsFormat.tex
finish 3.3.2.2

\textbf{Generating event phrases}.

@@

%\begin{comment}
\begin{table*}[ht]
\centering
\scalebox{0.76}{
\begin{tabular}{|cc|cc|cc|cc|cc|cc|}
\hline
\multicolumn{2}{|c|}{\textit{Aviation}} & \multicolumn{2}{c|}{\textit{Health}} & \multicolumn{2}{c|}{\textit{Middle East}} & \multicolumn{2}{c|}{\textit{Military}} & \multicolumn{2}{c|}{\textit{Mobile Phones}} & \multicolumn{2}{c|}{\textit{Video Games}} \\
\begin{tabular}[c]{@{}c@{}}Normal\\ States\end{tabular} & \begin{tabular}[c]{@{}c@{}}Topical\\ Words\end{tabular} & \begin{tabular}[c]{@{}c@{}}Normal\\ States\end{tabular} & \begin{tabular}[c]{@{}c@{}}Topical\\ Words\end{tabular} & \begin{tabular}[c]{@{}c@{}}Normal\\ States\end{tabular} & \begin{tabular}[c]{@{}c@{}}Topical\\ Words\end{tabular} & \begin{tabular}[c]{@{}c@{}}Normal\\ States\end{tabular} & \begin{tabular}[c]{@{}c@{}}Topical\\ Words\end{tabular} & \begin{tabular}[c]{@{}c@{}}Normal\\ States\end{tabular} & \begin{tabular}[c]{@{}c@{}}Topical\\ Words\end{tabular} & \begin{tabular}[c]{@{}c@{}}Normal\\ States\end{tabular} & \begin{tabular}[c]{@{}c@{}}Topical\\ Words\end{tabular} \\ 
\hline
aircraft & air\scriptsize(3253) & health & weight\scriptsize(16344) & al & \textcolor{red}{\textit{\#syria}}\scriptsize(4212) & army & killed\scriptsize(4055)  & android & iphone\scriptsize (13674) & game & games\scriptsize(8812) \\ 
air & plane & patients & loss & israel & \textcolor{red}{\textit{\#bahrain}} & military & news & mobile & apple & player & liked \\ 
airport & flight & medical & diet & iran & people & air & \textcolor{red}{\textit{\#libya}}\scriptsize(3503) & nokia & android & playstation & free \\ 
flight & time & disease & health & arab & israel & command & libya & ios & app & gameplay & xbox \\
airline & airlines & treatment & cancer & israeli & police & force & rebels & phone & ipad & nintendo & 360 \\
airlines & news & hospital & lose & egypt & \textcolor{red}{\textit{\#libya}}\scriptsize(2557) & regiment & people & samsung & samsung & games & playing \\
aviation & boat & patient & fat & egyptian & \#egypt & forces & police & game & mobile & players & played \\
flying & airport & clinical & tips & ibn & news & squadron & war & app & blackberry & xbox &iphone\scriptsize(2820)\\
pilot & force & symptoms & treatment & jerusalem & \#israel & infantry & libyan & iphone & tablet & mode & time\\
squadron & fly & cancer & body & syria & world & battle & attack & htc & apps & arcade & \textcolor{red}{\textit{ps3}}\\
\hline
\end{tabular}
}
\caption{History States extracted from Wikipedia and topical words learned from HS-Prior-LDA}
\label{tbl:historyStates}
\end{table*}
%\end{comment}

>>>>

\textbf{Generating event phrases}. 
In the set of event's candidate words \(\mathcal{B}_{c,t}\), some words appear together and should be grouped into event phrases.
For example, there are six bursty words in \(\mathcal{B}_{military,2011-07-28}\) belonging to two event phrases \textit{``Ft, Hood, attack"} and \textit{``Libyan, rebel, gunned"} in the time window 2011-07-28 to represent the events happened to the US military establishment and the Libyan rebel respectively.

In order to group the bursty words together, we  construct the directed weighted graph \(\mathcal{G}_{c,t}=(\mathcal{B}_{c,t},\mathcal{E}_{c,t})\), where \(\mathcal{E}_{c,t}=\{(a,b,PMI(a,b))|a \in \mathcal{B}_{c,t}, b \in \mathcal{B}_{c,t}, PMI(a,b)>0 \}\). 
The graph \(\mathcal{G}_{c,t}\) means the words in \(\mathcal{B}_{c,t}\) are connected if and only if their PMI score in the given time window's microblogs is over 0.

@@

\begin{table*}[ht]
\centering
\scalebox{0.76}{
\begin{tabular}{|cc|cc|cc|cc|cc|cc|}
\hline
\multicolumn{2}{|c|}{\textit{Aviation}} & \multicolumn{2}{c|}{\textit{Health}} & \multicolumn{2}{c|}{\textit{Middle East}} & \multicolumn{2}{c|}{\textit{Military}} & \multicolumn{2}{c|}{\textit{Mobile Phones}} & \multicolumn{2}{c|}{\textit{Video Games}} \\
\begin{tabular}[c]{@{}c@{}}Normal\\ States\end{tabular} & \begin{tabular}[c]{@{}c@{}}Topical\\ Words\end{tabular} & \begin{tabular}[c]{@{}c@{}}Normal\\ States\end{tabular} & \begin{tabular}[c]{@{}c@{}}Topical\\ Words\end{tabular} & \begin{tabular}[c]{@{}c@{}}Normal\\ States\end{tabular} & \begin{tabular}[c]{@{}c@{}}Topical\\ Words\end{tabular} & \begin{tabular}[c]{@{}c@{}}Normal\\ States\end{tabular} & \begin{tabular}[c]{@{}c@{}}Topical\\ Words\end{tabular} & \begin{tabular}[c]{@{}c@{}}Normal\\ States\end{tabular} & \begin{tabular}[c]{@{}c@{}}Topical\\ Words\end{tabular} & \begin{tabular}[c]{@{}c@{}}Normal\\ States\end{tabular} & \begin{tabular}[c]{@{}c@{}}Topical\\ Words\end{tabular} \\ 
\hline
aircraft & air\scriptsize(3253) & health & weight\scriptsize(16344) & al & \textcolor{red}{\textit{\#syria}}\scriptsize(4212) & army & killed\scriptsize(4055)  & android & iphone\scriptsize (13674) & game & games\scriptsize(8812) \\ 
air & plane & patients & loss & israel & \textcolor{red}{\textit{\#bahrain}} & military & news & mobile & apple & player & liked \\ 
airport & flight & medical & diet & iran & people & air & \textcolor{red}{\textit{\#libya}}\scriptsize(3503) & nokia & android & playstation & free \\ 
flight & time & disease & health & arab & israel & command & libya & ios & app & gameplay & xbox \\
airline & airlines & treatment & cancer & israeli & police & force & rebels & phone & ipad & nintendo & 360 \\
airlines & news & hospital & lose & egypt & \textcolor{red}{\textit{\#libya}}\scriptsize(2557) & regiment & people & samsung & samsung & games & playing \\
aviation & boat & patient & fat & egyptian & \#egypt & forces & police & game & mobile & players & played \\
flying & airport & clinical & tips & ibn & news & squadron & war & app & blackberry & xbox &iphone\scriptsize(2820)\\
pilot & force & symptoms & treatment & jerusalem & \#israel & infantry & libyan & iphone & tablet & mode & time\\
squadron & fly & cancer & body & syria & world & battle & attack & htc & apps & arcade & \textcolor{red}{\textit{ps3}}\\
\hline
\end{tabular}
}
\caption{History States extracted from Wikipedia and topical words learned from HS-Prior-LDA}
\label{tbl:historyStates}
\end{table*}
